A Linear Regression Model for Predicting MSDN Forums Votes

### 2018-10-31 forums/postScraping/msdn.forums.rmd
new html page

```{r}
fit200 = lm( v200 ~ vc200 + rc200, data = vcrcv)
summary(fit200)
cat('Confidence Interval ',confint(fit200))
summary(fit200)$coefficients

@@

```{r}
fit1000 = lm( v1000 ~ vc1000 + rc1000, data = vcrcv)
summary(fit1000)
cat('Confidence Interval ',confint(fit1000))
summary(fit1000)$coefficients

@@

```{r}
qqnorm(fit1000$residuals)
qqline(fit1000$residuals)
plot(fit1000)
#influencePlot(fit1000)
```

@@

```{r}
fit2000 = lm( v2000 ~ vc2000 + rc2000, data = vcrcv)
summary(fit2000)
cat('Confidence Interval ',confint(fit2000))
summary(fit2000)$coefficients

@@

```{r}
qqnorm(fit2000$residuals)
qqline(fit2000$residuals)
plot(fit2000)
```

@@

```{r}
fitall = lm( v ~ vc + rc, data = vcrcv)
summary(fitall)
cat('Confidence Interval ',confint(fitall))
summary(fitall)$coefficients

@@

```{r}
qqnorm(log(fitall$residuals))
qqline(log(fitall$residuals))
plot(fitall)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE}
#The following plots are taking code from

@@

fit1000 = lm( v1000 ~ vc1000 + rc1000 , data = vcrcv)

pfit1  = RegressionPlots(fit1000)

pfit1
```

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE}
fit200 = lm( v200 ~ vc200 + rc200, data = vcrcv)
summary(fit200)
#cat('Confidence Interval ',confint(fit200))
summary(fit200)$coefficients

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
fit1000 = lm( v1000 ~ vc1000 + rc1000, data = vcrcv)
summary(fit1000)
#cat('Confidence Interval ',confint(fit1000))
summary(fit1000)$coefficients

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
qqnorm(fit1000$residuals)
qqline(fit1000$residuals)
plot(fit1000)
#influencePlot(fit1000)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
fit2000 = lm( v2000 ~ vc2000 + rc2000, data = vcrcv)
summary(fit2000)
#cat('Confidence Interval ',confint(fit2000))
summary(fit2000)$coefficients

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
qqnorm(fit2000$residuals)
qqline(fit2000$residuals)
plot(fit2000)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
fitall = lm( v ~ vc + rc, data = vcrcv)
summary(fitall)
#cat('Confidence Interval ',confint(fitall))
summary(fitall)$coefficients

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
qqnorm(log(fitall$residuals))
qqline(log(fitall$residuals))
plot(fitall)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
#The following plots are taking code from

@@

fit200_ = lm( v200 ~ vc200 + rc200 , data = vcrcv)

pfit200  = RegressionPlots(fit200_)

pfit200
```
